|

### 2023-01-31 paper.Rmd
autogit

REG_TIME <- 5076.448
PT_TIME <- 14706.465
PT_TIME_NOSAMPLE <- 12536.889
```

@@

To investigate the strong negative impact of pre-training on DAE-GP runtime, I first studied the influence of pre-training on the median number of training epochs that had to be spend at each generation for the training of the DAE-LSTM models $M_g$. Figure \@ref(fig:airfoil-trainingEpochs) shows that pre-training, as expected, strongly reduces the number of training epochs that had to be executed at each generation until the termination condition was reached. By reducing the number of training epochs, pre-training should therefore reduce the runtime of DAE-GP.

@@

>>>>

REG_TIME <- 5076.448
PT_TIME <- 14706.465
PT_TIME_NOSAMPLE <- 12536.889

REG_MEDIAN_EPOCHSTRAINED <- 122.0
PT_MEDIAN_EPOCHSTRAINED <- 53.5

REG_MEDIAN_SAMPLINGTIME <- 29.055806166997172
PT_MEDIAN_SAMPLINGTIME <- 198.4502993219976

@@

To investigate the strong negative impact of pre-training on DAE-GP runtime, I first studied the influence of pre-training on the median number of training epochs that had to be spend at each generation for the training of the DAE-LSTM models $M_g$. Figure \@ref(fig:airfoil-trainingEpochs) shows that pre-training, as expected, strongly reduces the number of training epochs that had to be executed at each generation until the termination condition was reached. By reducing the number of training epochs, pre-training should therefore have positive benefit on the runtime of DAE-GP.

@@

If we look at another time consuming operation in DAE-GP, the creation of new individuals by sampling the DAE-LSTM model $M_G$, we see one main reason for the large runtime increase by pre-training DAE-GP. Figure \@ref(fig:airfoil-SamplingTime) shows the median sampling time spend during each generation of the search and it clearly shows that pre-training does strongly increase the time spent on model sampling in comparison to regular DAE-GP

### 2023-01-31 paper.tex
autogit

Unfortunately, as shown in figure \ref{fig:airfoil-runtime-total}, for the experiment conducted on the airfoil dataset with 2 hidden layers a strong negative impact of pre-training can be observed for the median runtime of DAE-GP. If the time spend on pre-training is included into the total runtime, the median duration for pre-trained DAE-GP over all 10 runs increases by a factor of 2.897 from a median runtime of 5076.448 seconds for regular DAE-GP to 14706.47 seconds for the pre-trained algorithm. Even in the case where the time spend for pre-training is excluded from the total runtime, pre-training still increases the runtime of DAE-GP by a factor of 2.47 to 12536.89 seconds.

@@

@@

>>>>

Suprinsingly, as shown in figure \ref{fig:airfoil-runtime-total}, for the experiment conducted on the airfoil dataset with 2 hidden layers a strong negative impact of pre-training can be observed for the median runtime of DAE-GP. If the time spend on pre-training is included into the total runtime, the median duration for pre-trained DAE-GP over all 10 runs increases by a factor of 2.897 from a median runtime of 5076.448 seconds for regular DAE-GP to 14706.47 seconds for the pre-trained algorithm. Even in the case where the time spend for pre-training is excluded from the total runtime, pre-training still increases the runtime of DAE-GP by a factor of 2.47 to 12536.89 seconds.

@@

To investigate the strong negative impact of pre-training on DAE-GP runtime, I first studied the influence of pre-training on the median number of training epochs that had to be spend at each generation for the training of the DAE-LSTM models \(M_g\). Figure \ref{fig:airfoil-trainingEpochs} shows that pre-training, as expected, strongly reduces the number of training epochs that had to be executed at each generation until the termination condition was reached. By reducing the number of training epochs, pre-training should therefore have positive benefit on the runtime of DAE-GP.

@@

If we look at another time consuming operation in DAE-GP, the creation of new individuals by sampling the DAE-LSTM model \(M_G\), we see one main reason for the large runtime increase by pre-training DAE-GP. Figure \ref{fig:airfoil-SamplingTime} shows the median sampling time spend during each generation of the search and it clearly shows that pre-training does strongly increase the time spent on model sampling in comparison to regular DAE-GP
